Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2018-01-31 paper.tex
Move table to intro and add warning about time-dependence

%\subsubsection*{In what ways is this method limited?}
Ray tracing is ideally suited to problems requiring detailed knowledge of
radiation distribution functions over small regions of spacetime:
for example along a matter or radiation trajectory,
or over a small volume outside a source.

@@

\subsection{Neutrino Oscillations at High Neutrino Densities}
\label{ssec:V_nunu}
In this section we examine the importance of elastic scattering in neutrino
flavor oscillation above the hypermassive neutron star--disk configuration
presented in Sec.~\ref{ssec:test_disk_comparison}.
Our treatment of the flavor evolution equation assumes flat space and small fluid
velocities.
In consequence we treat some of gauge-dependent quantities inconsistently,
and we ignore potentially important features of relativistic flavor evolution
near compact objects \cite{yang2017-gr_nu_oscillations}.
We believe our treatment is sufficient, however, for the following qualitative
exploration.

>>>>

%\subsubsection*{In what ways is this method limited?}
Ray tracing is ideally suited to problems requiring detailed knowledge of
radiation distribution functions over small regions of spacetime:
for example along a matter or radiation trajectory,
or over a small volume outside a source.
Furthermore, our method is time-dependent, allowing us to compute radiation
fields in dynamical systems. But it is formulated as a post-processing step,
with the ray tracing computated on volume data saved in several steps
of the fluid evolution.
Thus for dynamical systems the memory demands can be prohibitively large.

@@

\subsection{Neutrino Oscillations at High Neutrino Densities}
\label{ssec:V_nunu}
In this section we examine the importance of elastic scattering in neutrino
flavor oscillation above the hypermassive neutron star--disk configuration
presented in Sec.~\ref{ssec:test_disk_comparison}.
Our treatment of the flavor evolution equation assumes flat space and small fluid
velocities.
In consequence we treat some of the gauge-dependent quantities inconsistently,
and we ignore potentially important features of relativistic flavor evolution
near compact objects \cite{yang2017-gr_nu_oscillations}.
We believe our treatment is sufficient, however, for the following qualitative
exploration.
